---
title: "Assignment 4"
author: "Sidney Gerst, Natalie Dornan"
date: "May 30, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}

#load packages
library(tidyverse)
library(janitor)
library(stargazer)

#load and tidy the data

hw4 <- read_csv("HW4Data.csv") %>%
  clean_names()

#abatement is quantity. the reduction from current carbon emissions


```

###1. Marginal Cost of Abatement

####Sector A
```{r include = FALSE, message= FALSE}

#Regression analysis for Sector A(how does the data look graphically?)
plot_a <- ggplot(hw4, aes(x = abatement, y = mc_a)) +
  geom_point() +
  geom_smooth()

plot_a #looks very linear

#bc the data looks linear, use a linear regression

lm_a <- lm(mc_a ~ abatement, data = hw4)

lm_a
# Coefficients:
# (Intercept)    abatement  
#     -8.6445       0.5768 

#store the coefficients 

int_a <- lm_a$coefficients[1]
slope_a <- lm_a$coefficients[2]


```

<br>
$Marginal~Cost~of~Abatement~Sector~A = `r slope_a`*q + `r int_a`$

<br>

####Sector B 
```{r include = FALSE, message= FALSE}

#Regression analysis for Sector B(how does the data look graphically?)
plot_b <- ggplot(hw4, aes(x = abatement, y = mc_b)) +
  geom_point() +
  geom_smooth()

plot_b #looks very logistic, but sam is going to use a linear model so we will as well !

#if we really want to we can use a logit regression LATER

lm_b <- lm(mc_b ~ abatement, data = hw4)

lm_b
# Coefficients:
# (Intercept)    abatement  
#      9.3177       0.1987 

#store the coefficients 

int_b <- lm_b$coefficients[1]
slope_b <- lm_b$coefficients[2]


```

<br>
$Marginal~Cost~of~Abatement~Sector~B = `r slope_b`*q + `r int_b`$

<br>

####Sector C
```{r include= FALSE, message= FALSE}

#Regression analysis for Sector B(how does the data look graphically?)
plot_c <- ggplot(hw4, aes(x = abatement, y = mc_c)) +
  geom_point() +
  geom_smooth()

plot_c #looks very exponetial, but again, Sam said he was going to use lineal for all to make it easier on us later



lm_c <- lm(mc_c ~ abatement, data = hw4)

lm_c
# Coefficients:
# (Intercept)    abatement  
#    -11.6550       0.7838 

#store the coefficients 

int_c <- lm_c$coefficients[1]
slope_c <- lm_c$coefficients[2]



```

<br>
$Marginal~Cost~of~Abatement~Sector~C = `r slope_c`*q + `r int_c`$

<br>

####Sector D
```{r include=FALSE, message=FALSE}

#Regression analysis for Sector B(how does the data look graphically?)
plot_d <- ggplot(hw4, aes(x = abatement, y = mc_d)) +
  geom_point() +
  geom_smooth()

plot_d #looks very exponetial, but again, Sam said he was going to use lineal for all to make it easier on us later



lm_d <- lm(mc_d ~ abatement, data = hw4)

lm_d
# Coefficients:
# (Intercept)    abatement  
#      9.6875       0.2599  

#store the coefficients 

int_d <- lm_d$coefficients[1]
slope_d <- lm_d$coefficients[2]


```

<br>
$Marginal~Cost~of~Abatement~Sector~D = `r slope_d`*q + `r int_c`$

<br>

####Table of the regression coefficients 
```{r echo = FALSE, results = 'asis'}
#Stargazer table for the regressions

mc_table <- stargazer(lm_a, lm_b, lm_c, lm_d,
                          type = 'html', 
                          #single.row = TRUE,
                          align = TRUE,
                          title = "Table 1. Marginal abatement cost function for each sector.",
                          dep.var.labels = c("A", "B","C","D"), 
                          covariate.labels = c("Abatement", "Constant"),
                          add.lines = list(c("AIC", round(AIC(lm_a),1), round(AIC(lm_b),1), round(AIC(lm_c),1), round(AIC(lm_d),1))))


```

<br>
 
####Plot all Abatement Curves 
```{r echo=FALSE, message=FALSE}

# gather df so graphing is easier
# Marginal Abatement Cost dataframe
mac_df <- gather(hw4, key = "sector", value = "marginal_cost", "mc_a", "mc_b", "mc_c", "mc_d")



# graph it!
# can change line/point colors if we want
cols <- c("mc_a" = "hotpink1", "mc_b" = "royalblue1", "mc_c" = "seagreen3", "mc_d" = "coral1")
labels <- c("mc_a" = "A", "mc_b" = "B", "mc_c" = "C", "mc_d" = "D")


all_curves <- ggplot(mac_df, aes(x = abatement, y = marginal_cost)) +
  geom_point(aes(color = sector)) +
  geom_smooth(aes(color = sector), se = FALSE, method = lm) +
#  facet_grid(~sector) +
  scale_color_manual(values = cols,
                     labels = labels,
                     name = "Sector") + 
  theme_classic() + 
  labs(x = "Carbon Abatement (tons)", y = "Abatement Cost ($/ton)")
all_curves


#need to figure out how to plot multiple regressions onto one plot
# no <- qplot(x=mc_d, y=abatement, data=hw4)+
#   geom_abline(aes(intercept=int_a, slope=slope_a, col = "red"), data=lm_a) +
#   geom_abline(aes(intercept = int_b, slope=slope_b, col = "green"), data= lm_b) +
#   geom_abline(aes(intercept = int_c, slope = slope_c, col = "blue"), data= lm_c) +
#   geom_abline(aes(intercept = int_d, slope = slope_d, col = "yellow"), data = lm_d) +
#   theme_bw()
# 
# no


```




###2. Demand Curves of carbon emissions

<br>

#####Sector A
```{r include=FALSE}

#emissions for sector A are 180. we need to make a sequence from 0-180 by 10
quant_a <- seq(0,180,by=10)


#create a function for sector A demand curve 

demand_a <- function(q){
  (slope_a*(180-q)) + int_a
}

# Derive demand curve using the values above
d_a <- demand_a(quant_a)

#willing to pay 95.2 for the first ton of emissions 

# Graph it to see if this worked....
curve(demand_a, from=0, to=180, xlab = "x", ylab = "y")


```

 
Plugging in 0 for q will result in the willingness to pay for the right to pollute the first unit.
Sector A:  $Price~of~Emissions = `r slope_a`*(180-q) + `r int_a`$  
$Willingness~to~Pay~for~First~Unit = \$95.2$ 

<br>

#####Sector B
```{r include = FALSE }
#emissions for sector A are 180. we need to make a sequence from 0-180 by 10
quant_b <- seq(0,200,by=10)


#create a function for sector A demand curve 

demand_b <- function(q){
  (slope_b*(200-q)) + int_b
}

# Derive demand curve using the values above
d_b <- demand_b(quant_b)

#willing to pay 95.2 for the first ton of emissions 

# Graph it to see if this worked....
curve(demand_b, from=0, to=200, xlab = "x", ylab = "y")
```

  
$Price~of~Emissions = `r slope_b`*(180-q) + `r int_b`$  
$Willingness~to~Pay~for~First~Unit = \$49.1$ 

<br>

#####Sector C
```{r include = FALSE}
#emissions for sector A are 180. we need to make a sequence from 0-180 by 10
quant_c <- seq(0,220,by=10)


#create a function for sector A demand curve 

demand_c <- function(q){
  (slope_c*(220-q)) + int_c}

# Derive demand curve using the values above
d_c <- demand_c(quant_c)

#willing to pay 95.2 for the first ton of emissions 

# Graph it to see if this worked....
curve(demand_c, from=0, to=220, xlab = "x", ylab = "y")
```

$Price~of~Emissions = `r slope_c`*(180-q) + `r int_c`$  
$Willingness~to~Pay~for~First~Unit = \$161$ 

<br>

#####Sector D
```{r include = FALSE }
#emissions for sector A are 180. we need to make a sequence from 0-180 by 10
quant_d <- seq(0,300,by=10)


#create a function for sector A demand curve 

demand_d <- function(q){
  (slope_d*(300-q)) + int_d
}

# Derive demand curve using the values above
d_d <- demand_d(quant_d)

#willing to pay 95.2 for the first ton of emissions 

# Graph it to see if this worked....
curve(demand_d, from=0, to=300, xlab = "x", ylab = "y")

```

$Price~of~Emissions = `r slope_d`*(180-q) + `r int_d`$  
$Willingness~to~Pay~for~First~Unit = \$87.7$

<br>

####Combined Demand Curves
```{r echo = FALSE, warning=FALSE}

#Plot the demands on the same chart
#"mc_a" = "hotpink1", "mc_b" = "royalblue1", "mc_c" = "seagreen3", "mc_d" = "coral1"
cols_demand <- c("hotpink1", "royalblue1", "seagreen3", "coral1")
labels_demand <- c("A", "B", "C", "D")
demand_graph <- ggplot(data.frame(x=c(0,350)), aes(x=x)) + # data.frame gives ggplot something to graph
  stat_function(fun=demand_a, geom = "line", aes(color = "A"), size = 1) +
  stat_function(fun=demand_b, geom = "line", aes(color = "B"), size = 1) +
  stat_function(fun=demand_c, geom = "line", aes(color = "C"), size = 1) +
  stat_function(fun=demand_d, geom = "line", aes(color = "D"), size = 1) +
  scale_y_continuous(limits= c(0,175), expand = c(0,0)) +
  scale_x_continuous(limits= c(0, 400), expand = c(0,0)) +
  scale_color_manual(values = cols_demand,
                     labels = labels_demand,
                     name = "Sector") + 
  theme_classic() + 
  labs(x = "Carbon Abatement (tons)", y = "Abatement Cost ($/ton)")

demand_graph


```


<br> 

###3. Country X

#####A. Cap on Carbon. 
```{r include = FALSE}

#aggregate the costs of A, B, and C
#create functions of individual cost curves
lm_func_a <- function(q){
  slope_a*q + int_a
}



lm_func_b <- function(q){
  slope_b*q +int_b
}

lm_func_c <- function(q){
  slope_c*q + int_c
}

countryx <- function(q){
  
  lm_func_a(q) + lm_func_b(q) + lm_func_c(q)
  
}

curve(countryx, from=0, to=600, xlab = "x", ylab = "y")


```



```{r echo = FALSE }
#THIS IS THE AGGREGATE COST OF ABATEMENT  

#aggregate horizontally
slope_x = slope_a * slope_b + slope_a * slope_c + slope_b * slope_c
agg_y_int_x = (int_a*slope_b*slope_c/slope_x) + (int_b*slope_a*slope_c/slope_x) + (int_c*slope_b*slope_a/slope_x)
agg_coeff_x = (slope_a*slope_b*slope_c/slope_x)


#create the aggregate function
agg_abate_x <- function(q){
  agg_coeff_x*q + agg_y_int_x
}


#integratethe lm functions to find the total cost of a cap on carbon

costA_X <- integrate(lm_func_a, 0, 100)$value
costB_X <- integrate(lm_func_b, 0, 100)$value
costC_X <- integrate(lm_func_c, 0, 100)$value
cost_total <- costA_X + costB_X + costC_X






```


1. Total Cost of Carbon Cap   

$Total~Cost = `r round(cost_total, digits=2)`$   

2. Cost to each Sector 

$Cost~to~Sector~A = `r round(costA_X, digits=2)`$    

$Cost~to~Sector~B = `r round(costB_X, digits=2)`$    

$Cost~to~Sector~C = `r round(costC_X, digits=2)`$ 

3. There is no tax revenue with a cap on carbon

<br>

#####B. Tax on Carbon
```{r echo = FALSE }

#find the price at 300 tons of abatement for each sector 
tax_price <- agg_abate_x(300) #$39.4 


## abatement

unit_A <- (tax_price - int_a)/slope_a # 83.3
unit_B <- (tax_price - int_b)/slope_b # 151
unit_C <- (tax_price - int_c)/slope_c # 65.2

#solve the benefit for b, tax for carbon
costtax_A_X <- integrate(lm_func_a, 0, unit_A)$value  #2019,76
costtax_B_X <- integrate(lm_func_b, 0, unit_B)$value  #1925.49
costtax_C_X <- integrate(lm_func_c, 0, unit_C)$value  #2753.63
costtax_total <- costtax_A_X + costtax_B_X + costtax_C_X  #5879.81
tax_revenue_X <- 300*tax_price  #11,828


```


1. Total Cost of Carbon Tax   

$Total~Cost = `r round(costtax_total, digits=2)`$   

2. Cost to each Sector 

$Cost~to~Sector~A = `r round(costtax_A_X, digits=2)`$    

$Cost~to~Sector~B = `r round(costtax_B_X, digits=2)`$    

$Cost~to~Sector~C = `r round(costtax_C_X, digits=2)`$ 

3. Total Tax Revenue

$Total~Tax~Revenue = `r round(tax_revenue_X, digits=2)`$

<br>

#####C. Cap and Trade
```{r echo = FALSE }

## Need to find trading that brings abatement for all countries to 100 under optimal conditions

##Sector A
#abates by 83.3, buys 16.7 from Sector B

costA_cap <- integrate(lm_func_a, 0, unit_A)$value + (16.7*tax_price)

##Sector B
#abates by 151.5, sells 51.5 to A and C   

costB_cap <- integrate(lm_func_b, 0, unit_B)$value - (51.5*tax_price)

##Sector C
#abates by 65.2, buys 34.8 from Sector B

costC_cap <- integrate(lm_func_c, 0, unit_C)$value + (34.8*tax_price)

#integratethe lm functions to find the total cost of a cap on carbon


cost_total_cap <- costA_cap + costB_cap + costC_cap

```

1. Total Cost of Carbon Cap and Trade

$Total~Cost = `r round(cost_total_cap, digits=2)`$

2. Cost to each sector 

$Cost~to~Sector~A = `r round(costA_cap, digits=2)`$    

$Cost~to~Sector~B = `r round(costB_cap, digits=2)`$    

$Cost~to~Sector~C = `r round(costC_cap, digits=2)`$

3. Total Tax Revenue. Not applicable, no tax in Cap and Trade.

<br>

###4. Country Y
```{r include = FALSE}

#Want to find out if Country Y (Sector D ) has an incentive to go into County X's Market
#Place 300 into Sector D's ln function

lm_func_d <- function(q){
  slope_d*q + int_d
}

#this is for the last unit. We want the first unit
countryY <- lm_func_d(300) #87.7

#aggregate demand for ABCD
slopeY <- slope_a*slope_b*slope_c + slope_d*slope_b*slope_c + slope_a*slope_d*slope_c + slope_a*slope_b*slope_d
agg_y_int = (int_a*slope_b*slope_c*slope_d/slopeY) + (int_b*slope_a*slope_c*slope_d/slopeY) + (int_c*slope_b*slope_a*slope_d/slopeY) + (int_d*slope_b*slope_c*slope_a/slopeY)
agg_coeff_Y = (slope_a*slope_b*slope_c*slope_d/slopeY)

#the aggregate function
agg_abate_Y <- function(q){
  agg_coeff_Y*q + agg_y_int
}

#optimal tax
tax_price_Y <- agg_abate_Y(300)
unit_a_Y <- (tax_price_Y - int_a)/slope_a
unit_b_Y <- (tax_price_Y - int_b)/slope_b
unit_c_Y <- (tax_price_Y - int_c)/slope_c
unit_d_Y <- (tax_price_Y - int_d)/slope_d

int_Y <- (int_d - agg_y_int)/agg_coeff_Y




#costs 
cost_tax_a_Y <- integrate(lm_func_a, 0, unit_a_Y)$value
cost_tax_b_Y <- integrate(lm_func_b, 0, unit_b_Y)$value
cost_tax_c_Y <- integrate(lm_func_c, 0, unit_c_Y)$value
cost_tax_d_Y <- integrate(lm_func_d, 0, unit_d_Y)$value


#cap and trade with country y and country x and total costs 
A_trade_xy <- (180-unit_a_Y-80)
B_trade_xy <- (200-unit_b_Y-100)
C_trade_xy <-(220-unit_c_Y-120)
D_trade_xy <-(300-unit_d_Y-300)

#figure out how much to sell/buy
A_trans_XY <- A_trade_xy*tax_price_Y #A buy this
B_trans_XY <- B_trade_xy*tax_price_Y #B sells this 
C_trans_XY <- C_trade_xy*tax_price_Y #C buys this 
D_trans_XY <- D_trade_xy*tax_price_Y #D sells this

#find the final abatement 
A_trade_nc_XY <- cost_tax_a_Y + A_trans_XY
B_trade_nc_XY <- cost_tax_b_Y + B_trans_XY
C_trade_nc_XY <- cost_tax_c_Y + C_trans_XY
D_trade_nc_XY <- cost_tax_d_Y + D_trans_XY

#the totals
total_costs_x_ABCD <- A_trade_nc_XY + B_trade_nc_XY + C_trade_nc_XY + D_trade_nc_XY
total_costs_y_ABCD <- D_trade_nc_XY



```

 The total cost of country X is $`r round(total_costs_x_ABCD, digits = 2)` and the total cost for country Y is \$`r round(total_costs_y_ABCD, digits = 2)`. Because Y is negative, they have benefits to gain from entering the cap and trade program with country X.
 
A will buy `r round(A_trans_XY, digits = 2)` with a final abatement of `r round(A_trade_nc_XY, digits = 2)` 

B will sell `r round(B_trans_XY, digits = 2)` with a final abatement of `r round(B_trade_nc_XY, digits = 2)`

C will buy `r round(C_trans_XY, digits = 2)` with a final abatement of `r round(C_trade_nc_XY, digits = 2)`

D will sell `r round(D_trans_XY, digits = 2)` with a final abatement of `r round(D_trade_nc_XY, digits = 2)`
